Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models

### 2024-01-16 related.tex
修改related work

<<<<<<< HEAD

\section{Related Work}
\label{sec:related}
In this section, we briefly summarize previous work on how Large Language Models (LLMs) such as the GPT series can be utilized as sources of knowledge and content generators to enhance and enrich text data in various application scenarios.
\subsection{Interaction with LLMs}
Recent research emphasizes the significance of extracting knowledge from Large Language Models (LLMs) in domains characterized by limited knowledge base coverage~\citep{fang2021leveraging}.
GPT3Mix~\citep{yoo2021gpt3mix} extends the utility of LLMs to text data augmentation, thereby elevating the performance of machine learning models. 
AugGPT~\citep{dai2023auggpt} further contributes to natural language processing tasks in scenarios with constrained data by generating new textual data through interactions with ChatGPT.

@@

More recently, SpanQualifier~\cite{huang2023qualifier} improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
Iterative Extractor~\cite{zhang2023many} introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
While these methods leverage powerful context encoders (PrLMs) with good multi-span answer extraction performance, they fall short in fully harnessing external knowledge, limiting their text comprehension abilities.
LIQUID~\cite{lee2023liquid} was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model. However, its focus on list QA data narrows the scope of knowledge and lacks specificity, reducing efficiency.
In contrast, AUG significantly advances the field by efficiently enhancing model training. It achieves this by leveraging interactions with a large language model to acquire contextually relevant knowledge directly tied to the data, which can be seamlessly incorporated into the finetuning.

\subsection{Interaction with LLMs}

>>>>

\section{Related Work}
\label{sec:related}
This section briefly covers past research on employing Large Language Models (LLMs) like GPT for knowledge enhancement in diverse applications, emphasizing different approaches in extractive Reading Comprehension (RC) tasks.

\subsection{Interaction with LLMs}
Recent research emphasizes the significance of extracting knowledge from Large Language Models (LLMs) in domains characterized by limited knowledge base coverage~\citep{fang2021leveraging}.
GPT3Mix~\citep{yoo2021gpt3mix} extends the utility of LLMs to text data augmentation, thereby elevating the performance of machine learning models. 
AugGPT~\citep{dai2023auggpt} further contributes to natural language processing tasks in scenarios with constrained data by generating new textual data through interactions with ChatGPT.

@@

More recently, SpanQualifier~\citep{huang2023qualifier} improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
Iterative Extractor~\citep{zhang2023many} introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
While these methods leverage powerful context encoders (PrLMs) with good multi-span answer extraction performance, they fall short in fully harnessing external knowledge, limiting their text comprehension abilities.
LIQUID~\citep{lee2023liquid} was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model. However, its focus on list QA data narrows the scope of knowledge and lacks specificity, reducing efficiency.
In contrast, AUG significantly advances the field by efficiently enhancing model training. It achieves this by leveraging interactions with a large language model to acquire contextually relevant knowledge directly tied to the data, which can be seamlessly incorporated into the finetuning.
